---
title: "Grid plot with R"
title-prefix: "UNHCR Dataviz Platform"
author:
  - "Cedric Vidonne"
  - "Lei Chen"
output:
  html_document:
    theme: null
    self_contained: false
    highlight: "pygments"
    includes:
      in_header:
        - "../rmd_includes/r_part_to_a_whole_head.html"
        - "../rmd_includes/in_head.html"
      before_body: "../rmd_includes/header.html"
      after_body:
        - "../rmd_includes/r_part_to_a_whole.html"
        - "../rmd_includes/footer.html"
        - "../rmd_includes/footer_script.html"
params:
  tool: R
  chart_type: Grid plot
  url_cat: part_to_a_whole
  url_chart: grid-plot
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  base.dir = "../../assets/img/tools/",
  base.url = "../../assets/img/tools/"
)
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = paste0(tolower(params$tool), "/"),
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  dev = "svglite",
  fig.showtext = TRUE,
  fig.retina = 2,
  dpi = 300
)
library(unhcrthemes)
library(tidyverse)
```

<main id="tools" class="container mt-5">

<!-- Breadcrumb is filled automatically with the text from Title and Tool parameter in YAML --> 
<nav aria-label="breadcrumb">
    <ol class="breadcrumb">
        <li class="breadcrumb-item"><a href="../../">Home</a></li>
        <li class="breadcrumb-item"><a href="../">Tools</a></li>
        <li class="breadcrumb-item"><a href="../`r tolower(params$tool)`/">`r params$tool`</a></li>
        <li class="breadcrumb-item active" aria-current="page">`r rmarkdown::metadata$title`</li>
    </ol>
</nav>

<!-- Intro header --> 
<div class="my-5 text-center">

## `r rmarkdown::metadata$title`

<div class="row justify-content-center">
<div class="col-lg-8">

<!-- Only text to change below, the rest comes from the YAML --> 
A grid plot is a type of visualization that shows progress towards a target or a completion percentage. The value (percentage) is represented by a grid of coloured small cells. Multiple grid plot can be put together to show the differences among percentages.

More about: <a href="../../chart_gallery/`r params$url_cat`.html#`r params$url_chart`">`r params$chart_type`</a>

</div>
</div>
</div>


----

<!-- Beginning of section, should be preceded by hr (----) --> 
<section class="my-5">

### Grid plot small muliples

<div class="row">

<!-- First column for large screen --> 
<div class="col-lg-6">

```{r grid_code, echo=TRUE, fig.show = 'hide', warning=FALSE, message=FALSE}
# Loading required packages
library(unhcrthemes)
library(tidyverse)
# install.packages("waffle", repos = "https://cinc.rud.is")
library(waffle)


# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/part_to_a_whole/gridplot_multiple.csv") |> 
  mutate(coping_short = stringr::str_wrap(coping_mechanism,
                                          width = 25))



# Plot
ggplot(df) +
  geom_waffle(aes(fill = category, values = households_num),
              make_proportional = TRUE,
              flip = TRUE,
              color = "white",
              size = .5
              ) +
  labs(
    title = "Top 5 negative coping mechanisms",
    subtitle = "Percentage of households",
    caption = "Source: UNHCR Post-distribution Monitoring for Cash-based Assistance, January 2021\n© UNHCR, The UN Refugee Agency"
  ) +
  scale_fill_unhcr_d(palette = "pal_unhcr") +
  coord_equal() +
  facet_wrap(~coping_short, ncol = 2) +
  theme_unhcr(axis = FALSE, grid = FALSE, axis_text = FALSE, font_size = 13)
```

</div>
<!-- End First column --->

<!-- Second column for large screen --> 
<div class="col-lg-6">


```{r grid_plot, ref.label= 'grid_code', echo=FALSE, error=FALSE, results='hide', out.width="100%", fig.height=10}
```

</div>
<!-- End Second column --->

</div>
</section>
<!-- End of section --->

<!-- To add sections just copy the whole code between the above section tag --->

</main>
