---
title: "Treemap with R"
title-prefix: "UNHCR Dataviz Platform"
author:
  - "Cedric Vidonne"
  - "Lei Chen"
output:
  html_document:
    theme: null
    self_contained: false
    highlight: "pygments"
    includes:
      in_header:
        - "../rmd_includes/r_part_to_a_whole_head.html"
        - "../rmd_includes/in_head.html"
      before_body: "../rmd_includes/header.html"
      after_body:
        - "../rmd_includes/r_part_to_a_whole.html"
        - "../rmd_includes/footer.html"
        - "../rmd_includes/footer_script.html"
params:
  tool: R
  chart_type: Treemap
  url_cat: part_to_a_whole
  url_chart: treemap
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  base.dir = "../../assets/img/tools/",
  base.url = "../../assets/img/tools/"
)
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = paste0(tolower(params$tool), "/"),
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  dev = "svglite",
  fig.showtext = TRUE,
  fig.retina = 2,
  dpi = 300
)
library(unhcrthemes)
library(tidyverse)
library(scales)
library(treemapify)
```

<main id="tools" class="container mt-5">

<!-- Breadcrumb is filled automatically with the text from Title and Tool parameter in YAML --> 
<nav aria-label="breadcrumb">
    <ol class="breadcrumb">
        <li class="breadcrumb-item"><a href="../../">Home</a></li>
        <li class="breadcrumb-item"><a href="../">Tools</a></li>
        <li class="breadcrumb-item"><a href="../`r tolower(params$tool)`/">`r params$tool`</a></li>
        <li class="breadcrumb-item active" aria-current="page">`r rmarkdown::metadata$title`</li>
    </ol>
</nav>

<!-- Intro header --> 
<div class="my-5 text-center">

## `r rmarkdown::metadata$title`

<div class="row justify-content-center">
<div class="col-lg-8">

<!-- Only text to change below, the rest comes from the YAML --> 
As a variation of a tree diagram, a treemap is meant to show hierarchical structure using the size of the rectangle to represent quantity. Each category is assigned a rectangle, with subcategories displayed inside the large rectangle, in proportionate size against each other. 

More about: <a href="../../chart_gallery/`r params$url_cat`.html#`r params$url_chart`">`r params$chart_type`</a>

</div>
</div>
</div>


----

<!-- Beginning of section, should be preceded by hr (----) --> 
<section class="my-5">

### Treemap

<div class="row">

<!-- First column for large screen --> 
<div class="col-lg-6">

```{r treemap_code, echo=TRUE, eval=FALSE}
# Loading required packages
library(unhcrthemes)
library(tidyverse)
library(treemapify)

# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/part_to_a_whole/treemap.csv")

# Plot
ggplot(
  df,
  aes(area = staff_number)
) +
  geom_treemap(
    color = "#FFFFFF",
    size = 1,
    fill = unhcr_pal(n = 1, "pal_blue"),
    start = "topleft"
  ) +
  geom_treemap_text(aes(label = paste0(
    round(100 * staff_number / sum(staff_number), 1),
    "%\n",
    region
  )),
  color = "#FFFFFF",
  size = 9,
  start = "topleft",
  family = "Lato"
  ) +
  labs(
    title = "UNHCR global workforce by region | 2021",
    caption = "Source: Define source here\n© UNHCR, The UN Refugee Agency"
  ) +
  theme_unhcr(
    axis = FALSE,
    axis_title = FALSE,
    grid = FALSE
  )
```

</div>
<!-- End First column --->

<!-- Second column for large screen --> 
<div class="col-lg-6">


```{r r_treemap, echo=FALSE, out.width="100%", fig.height=5.8, fig.alt="A treemap showing UNHCR global workforce by region | 2021"}
# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/part_to_a_whole/treemap.csv")

ggplot(df, aes(area = staff_number)) +
  geom_treemap(
    color = "#FFFFFF", size = 1,
    fill = unhcr_pal(n = 1, "pal_blue"), start = "topleft"
  ) +
  geom_treemap_text(aes(label = paste0(round(100 * staff_number / sum(staff_number), 1), "%\n", region)),
    color = "#FFFFFF", size = 13,
    start = "topleft", family = "Lato",
    padding.x = grid::unit(2, "mm"), padding.y = grid::unit(2, "mm")
  ) +
  labs(
    title = "UNHCR global workforce by region | 2021",
    caption = "Source: Define source here\n© UNHCR, The UN Refugee Agency"
  ) +
  theme_unhcr(font_size = 13, axis = FALSE, axis_title = FALSE, grid = FALSE)
```

</div>
<!-- End Second column --->

</div>
</section>
<!-- End of section --->

<!-- To add sections just copy the whole code between the above section tag --->

</main>
