---
title: "Boxplot with R"
title-prefix: "UNHCR Dataviz Platform"
author:
  - "Cedric Vidonne"
  - "Lei Chen"
output:
  html_document:
    theme: null
    self_contained: false
    highlight: "pygments"
    includes:
      in_header:
        - "../rmd_includes/r_distribution_head.html"
        - "../rmd_includes/in_head.html"
      before_body: "../rmd_includes/header.html"
      after_body:
        - "../rmd_includes/r_distribution.html"
        - "../rmd_includes/footer.html"
        - "../rmd_includes/footer_script.html"
params:
  tool: R
  chart_type: Boxplot
  url_cat: distribution
  url_chart: boxplot
---

```{r setup, include=FALSE}
knitr::opts_knit$set(
  base.dir = "../../assets/img/tools/",
  base.url = "../../assets/img/tools/"
)
knitr::opts_chunk$set(
  echo = FALSE,
  fig.path = paste0(tolower(params$tool), "/"),
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  comment = "#>",
  dev = "svglite",
  fig.showtext = TRUE,
  fig.retina = 2,
  dpi = 300
)
library(unhcrthemes)
library(tidyverse)
library(scales)
```

<main id="tools" class="container mt-5">

<!-- Breadcrumb is filled automatically with the text from Title and Tool parameter in YAML --> 
<nav aria-label="breadcrumb">
    <ol class="breadcrumb">
        <li class="breadcrumb-item"><a href="../../">Home</a></li>
        <li class="breadcrumb-item"><a href="../">Tools</a></li>
        <li class="breadcrumb-item"><a href="../`r tolower(params$tool)`/">`r params$tool`</a></li>
        <li class="breadcrumb-item active" aria-current="page">`r rmarkdown::metadata$title`</li>
    </ol>
</nav>


<!-- Intro header --> 
<div class="my-5 text-center">

## `r rmarkdown::metadata$title`

<div class="row justify-content-center">
<div class="col-lg-8">

<!-- Only text to change below, the rest comes from the YAML --> 
The boxplot uses boxes and lines to show the distributions of one or more groups of numeric data based on a 5-point summary of data points: the upperextreme (“maximum”), upper quartile (Q3), median, lower quartile (Q1), and lower extreme (minimum) values.

More about: <a href="../../chart_gallery/`r params$url_cat`.html#`r params$url_chart`">`r params$chart_type`</a>

</div>
</div>
</div>


----

<!-- Beginning of section, should be preceded by hr (----) --> 
<section class="my-5">

### Boxplot

<div class="row">

<!-- First column for large screen --> 
<div class="col-lg-6">

```{r boxplot_code, echo=TRUE, eval=FALSE}
# Loading required packages
library(unhcrthemes)
library(tidyverse)

# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/distribution/boxplot.csv")

# Plot
ggplot(df, aes(x = country, y = age)) +
  geom_boxplot(fill = unhcr_pal(n = 1, "pal_blue"),
               alpha = 0.3,
               color = unhcr_pal(n = 1, "pal_grey"),
               width = .5) +
  labs(
    title = "Refugees age distribution by country of asylum | 2020",
    caption = "Source: Data source here\n© UNHCR, The UN Refugee Agency",
    x = NULL,
    y = "Age"
  ) +
  scale_y_continuous(expand = expansion(c(0, 0.1)),
                     breaks = seq(0, 100, 10)) +
  theme_unhcr(grid = "Y")
```

</div>
<!-- End First column --->

<!-- Second column for large screen --> 
<div class="col-lg-6">


```{r r_boxplot, echo=FALSE, out.width="100%", fig.height=5.8, fig.alt="A boxplot showing age distribution | 2020"}
# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/distribution/boxplot.csv")

ggplot(df, aes(x = country, y = age)) +
  geom_boxplot(fill = unhcr_pal(n = 1, "pal_blue"),
               alpha = 0.4,
               color = unhcr_pal(n = 1, "pal_grey"),
               width = .5) +
  labs(
    title = "Refugees age distribution by country of asylum | 2020",
    caption = "Source: Data source here\n© UNHCR, The UN Refugee Agency",
    x = NULL,
    y = "Age"
  ) +
  scale_y_continuous(expand = expansion(c(0, 0.1)),
                     breaks = seq(0, 100, 10)) +
  theme_unhcr(font_size = 13, grid = "Y")
```

</div>
<!-- End Second column --->

</div>
</section>
<!-- End of section --->

---

<!-- Beginning of section, should be preceded by hr (----) --> 
<section class="my-5">

### Grouped boxplot

<div class="row">

<!-- First column for large screen --> 
<div class="col-lg-6">

```{r boxplot_group_code, echo=TRUE, eval=FALSE}
# Loading required packages
library(unhcrthemes)
library(tidyverse)

# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/distribution/boxplot.csv")

# Plot
ggplot(df, aes(x = country, y = age, fill = gender)) +
  geom_boxplot(alpha = 0.4,
               color = unhcr_pal(n = 1, "pal_grey"),
               width = .5) +
  labs(
    title = "Refugees age distribution and gender\nby country of asylum | 2020",
    caption = "Source: Data source here\n© UNHCR, The UN Refugee Agency",
    x = NULL,
    y = "Age"
  ) +
  scale_fill_unhcr_d(nmax = 3, order = c(2, 1)) +
  scale_y_continuous(expand = expansion(c(0, 0.1)),
                     breaks = seq(0, 100, 10)) +
  theme_unhcr(grid = "Y")
```

</div>
<!-- End First column --->

<!-- Second column for large screen --> 
<div class="col-lg-6">


```{r r_boxplot_group, echo=FALSE, out.width="100%", fig.height=5.8, fig.alt="A boxplot showing age distribution by gender | 2020"}
# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/distribution/boxplot.csv")

ggplot(df, aes(x = country, y = age, fill = gender)) +
  geom_boxplot(alpha = 0.4,
               color = unhcr_pal(n = 1, "pal_grey"),
               width = .5) +
  labs(
    title = "Refugees age distribution and gender\nby country of asylum | 2020",
    caption = "Source: Data source here\n© UNHCR, The UN Refugee Agency",
    x = NULL,
    y = "Age"
  ) +
  scale_fill_unhcr_d(nmax = 3, order = c(2, 1)) +
  scale_y_continuous(expand = expansion(c(0, 0.1)),
                     breaks = seq(0, 100, 10)) +
  theme_unhcr(font_size = 13, grid = "Y")
```

</div>
<!-- End Second column --->

</div>
</section>
<!-- End of section --->


<!-- To add sections just copy the whole code between the above section tag --->

</main>
