---
title: "Bubble chart with R"
title-prefix: "UNHCR Dataviz"
author: "IPDA/GDS"
output:
  html_document:
    theme: null
    self_contained: false
    highlight: "pygments"
    includes:
      in_header: "../rmd_includes/in_head.html"
      before_body: "../rmd_includes/header.html"
      after_body:
        - "../rmd_includes/r_correlation.html"
        - "../rmd_includes/footer.html"
        - "../rmd_includes/footer_script.html"
params:
  tool: R
  chart_type: Bubble chart
  url_cat: correlation
  url_chart: bubble
---

```{r setup, include=FALSE}
knitr::opts_knit$set(base.dir = "../../assets/img/tools/",
                     base.url = "../../assets/img/tools/")
knitr::opts_chunk$set(echo = FALSE,
                      fig.path= paste0(tolower(params$tool),"/"),
                      message = FALSE,
                      warning = FALSE,
                      collapse = TRUE,
                      comment = "#>",
                      dev = "svglite",
                      fig.showtext = TRUE,
                      fig.retina = 2,
                      dpi = 300)
library(unhcrthemes)
library(tidyverse)
library(scales)
library(ggrepel)
```

<main id="tools" class="container mt-5">

<!-- Breadcrumb is filled automatically with the text from Title and Tool parameter in YAML --> 
<nav aria-label="breadcrumb">
    <ol class="breadcrumb">
        <li class="breadcrumb-item"><a href="../../">Home</a></li>
        <li class="breadcrumb-item"><a href="../">Tools</a></li>
        <li class="breadcrumb-item"><a href="../`r tolower(params$tool)`/">`r params$tool`</a></li>
        <li class="breadcrumb-item active" aria-current="page">`r rmarkdown::metadata$title`</li>
    </ol>
</nav>


<!-- Intro header --> 
<div class="my-5 text-center">

## `r rmarkdown::metadata$title`

<div class="row justify-content-center">
<div class="col-lg-8">

<!-- Only text to change below, the rest comes from the YAML --> 
A bubble chart displays multi-dimensional data in a two-dimensional plot. It can be considered as a variation of the scatterplot, in which the dots are replaced with bubbles. However, unlike a scatterplot which has only two variables defined by the X and Y axis, on a bubble chart each data point (bubble) can be assigned with a third variable (by size of bubble) and a fourth variable (by colour of bubble)

More about: <a href="../../chart_gallery/`r params$url_cat`.html#`r params$url_chart`">`r params$chart_type`</a>

</div>
</div>
</div>


----

<!-- Beginning of section, should be preceded by hr (----) --> 
<section class="my-5">

### Bubble chart

<div class="row">

<!-- First column for large screen --> 
<div class="col-lg-6">

```{r bubble_code, echo=TRUE, eval=FALSE}
# Loading required packages
library(unhcrthemes)
library(tidyverse)
library(scales)
library(ggrepel)

# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/correlation/bubble.csv")

# Plot
ggplot(df, aes(x = refugee_number, y = idp_number)) +
  geom_point(aes(size = total_number), color = unhcr_pal(n = 1, "pal_blue"), alpha = 0.6) +
  scale_size(range = c(4, 16), name = "Total population", labels = label_number_si(),
             breaks = c(8e6, 10e6, 12e6)) +
  geom_text_repel(aes(label = region), size = 8/.pt) +
  labs(title = "Comparison of refugee and IDP population by region | 2021",
       y = "Number of IDPs",
       x = "Number of refugees",
       caption = "Source: UNHCR Refugee Data Finder\n© UNHCR, The UN Refugee Agency") +
  scale_x_continuous(labels = label_number_si()) +
  scale_y_continuous(labels = label_number_si(),
                     breaks = pretty_breaks(n = 6)) +
  coord_cartesian(clip = "off") +
  theme_unhcr(grid = "XY", axis = FALSE, axis_title = "xy", legend_title = TRUE)
```

</div>
<!-- End First column --->

<!-- Second column for large screen --> 
<div class="col-lg-6">


```{r r_bubble_chart, echo=FALSE, out.width="100%", fig.height=5.8}
# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/correlation/bubble.csv")

ggplot(df, aes(x = refugee_number, y = idp_number)) +
  geom_point(aes(size = total_number), color = unhcr_pal(n = 1, "pal_blue"), alpha = 0.6) +
  scale_size(range = c(4, 16), name = "Total population", labels = label_number_si(),
             breaks = c(8e6, 10e6, 12e6)) +
  geom_text_repel(aes(label = region), size = 11.5/.pt) +
  labs(title = "Comparison of refugee and IDP population by region | 2021",
       y = "Number of IDPs",
       x = "Number of refugees",
       caption = "Source: UNHCR Refugee Data Finder\n© UNHCR, The UN Refugee Agency") +
  scale_x_continuous(labels = label_number_si()) +
  scale_y_continuous(labels = label_number_si(),
                     breaks = pretty_breaks(n = 6)) +
  coord_cartesian(clip = "off") +
  theme_unhcr(font_size = 13, grid = "XY", axis = FALSE, axis_title = "xy", legend_title = TRUE)
```

</div>
<!-- End Second column --->

</div>
</section>
<!-- End of section --->

----

<!-- Beginning of section, should be preceded by hr (----) --> 
<section class="my-5">

### Bubble chart with colours

<div class="row">

<!-- First column for large screen --> 
<div class="col-lg-6">

```{r bubble_color_code, echo=TRUE, eval=FALSE}
# Loading required packages
library(unhcrthemes)
library(tidyverse)
library(scales)
library(ggrepel)

# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/correlation/bubble.csv")

# Order regions for visualization
df$region <- factor(df$region, levels = c("East and Horn of Africa and Great Lakes", "Southern Africa", "West and Central Africa", "Americas", "Asia and the Pacific", "Europe", "Middle East and North Africa"))

# Plot
ggplot(df, aes(x = refugee_number, y = idp_number)) +
  geom_point(aes(size = total_number, color = region),  alpha = 0.6) +
  scale_size(range = c(4, 16), name = "Total population", labels = label_number_si(),
             breaks = c(8e6, 10e6, 12e6)) +
  geom_text_repel(aes(label = region), size = 8/.pt) +
  labs(title = "Comparison of refugee and IDP population by region | 2021",
       y = "Number of IDPs",
       x = "Number of refugees",
       caption = "Source: UNHCR Refugee Data Finder\n© UNHCR, The UN Refugee Agency") +
  scale_x_continuous(labels = label_number_si()) +
  scale_y_continuous(labels = label_number_si(),
                     breaks = pretty_breaks(n = 6)) +
  scale_color_unhcr_d(palette = "pal_unhcr_region", guide = "none") +
  coord_cartesian(clip = "off") +
  theme_unhcr(grid = "XY", axis = FALSE, axis_title = "xy", legend_title = TRUE) +
  guides(size = guide_legend(override.aes = list(shape = 21)))
```

</div>
<!-- End First column --->

<!-- Second column for large screen --> 
<div class="col-lg-6">


```{r r_bubble_color_chart, echo=FALSE, out.width="100%", fig.height=5.8}
# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/correlation/bubble.csv")

# Order regions for visualization
df$region <- factor(df$region, levels = c("East and Horn of Africa and Great Lakes", "Southern Africa", "West and Central Africa", "Americas", "Asia and the Pacific", "Europe", "Middle East and North Africa"))

ggplot(df, aes(x = refugee_number, y = idp_number)) +
  geom_point(aes(size = total_number, color = region),  alpha = 0.6) +
  scale_size(range = c(4, 16), name = "Total population", labels = label_number_si(),
             breaks = c(8e6, 10e6, 12e6)) +
  geom_text_repel(aes(label = region), size = 11.5/.pt) +
  labs(title = "Comparison of refugee and IDP population by region | 2021",
       y = "Number of IDPs",
       x = "Number of refugees",
       caption = "Source: UNHCR Refugee Data Finder\n© UNHCR, The UN Refugee Agency") +
  scale_x_continuous(labels = label_number_si()) +
  scale_y_continuous(labels = label_number_si(),
                     breaks = pretty_breaks(n = 6)) +
  scale_color_unhcr_d(palette = "pal_unhcr_region", guide = "none") +
  coord_cartesian(clip = "off") +
  theme_unhcr(font_size = 13, grid = "XY", axis = FALSE, axis_title = "xy", legend_title = TRUE) +
  guides(size = guide_legend(override.aes = list(shape = 21)))
```

</div>
<!-- End Second column --->

</div>
</section>
<!-- End of section --->

<!-- To add sections just copy the whole code between the above section tag --->

</main>
