---
title: "100% stacked column chart with R"
title-prefix: "UNHCR  Dataviz"
author: "IPDA/GDS"
output:
  html_document:
    theme: null
    self_contained: false
    highlight: "pygments"
    includes:
      in_header: "../rmd_includes/in_head.html"
      before_body: "../rmd_includes/header.html"
      after_body:
        - "../rmd_includes/r_part_to_a_whole.html"
        - "../rmd_includes/footer.html"
        - "../rmd_includes/footer_script.html"
params:
  tool: R
  chart_type: 100% stacked column chart
  url_cat: part_to_a_whole
  url_chart: column-stacked-100perc
---

```{r setup, include=FALSE}
knitr::opts_knit$set(base.dir = "../../assets/img/tools/",
                     base.url = "../../assets/img/tools/")
knitr::opts_chunk$set(echo = FALSE,
                      fig.path= paste0(tolower(params$tool),"/"),
                      message = FALSE,
                      warning = FALSE,
                      collapse = TRUE,
                      comment = "#>",
                      dev = "svglite",
                      fig.showtext = TRUE,
                      fig.retina = 2,
                      dpi = 300)
library(unhcrthemes)
library(tidyverse)
library(scales)
```

<main id="tools" class="container mt-5">

<!-- Breadcrumb is filled automatically with the text from Title and Tool parameter in YAML --> 
<nav aria-label="breadcrumb">
    <ol class="breadcrumb">
        <li class="breadcrumb-item"><a href="../../">Home</a></li>
        <li class="breadcrumb-item"><a href="../">Tools</a></li>
        <li class="breadcrumb-item"><a href="../`r tolower(params$tool)`/">`r params$tool`</a></li>
        <li class="breadcrumb-item active" aria-current="page">`r rmarkdown::metadata$title`</li>
    </ol>
</nav>

<!-- Intro header --> 
<div class="my-5 text-center">

## `r rmarkdown::metadata$title`

<div class="row justify-content-center">
<div class="col-lg-8">

<!-- Only text to change below, the rest comes from the YAML --> 
100% stacked column charts are similar to stacked column charts in that categories are represented as vertical bars and series as components of those bars. However, in a 100% stacked column chart, each series bar represents the percentage of the whole to which it belongs, where the total (cumulative) of each stacked bar always equals 100%.

More about: <a href="../../chart_gallery/`r params$url_cat`.html#`r params$url_chart`">`r params$chart_type`</a>

</div>
</div>
</div>


----

<!-- Beginning of section, should be preceded by hr (----) --> 
<section class="my-5">

### 100% stacked column chart

<div class="row">

<!-- First column for large screen --> 
<div class="col-lg-6">

```{r column_stacked_100perc_code, echo=TRUE, eval=FALSE}
# Loading required packages
library(unhcrthemes)
library(tidyverse)
library(scales)

# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/part_to_a_whole/column_stacked_100perc.csv")

# Plot
ggplot(df) +
  geom_col(aes(x = year, y = percentage, fill = funding_type),
           width = 0.7, position = position_fill()) +
  scale_fill_unhcr_d(palette = "pal_unhcr") +
  scale_x_continuous(breaks = pretty_breaks(n = 9)) +
  scale_y_continuous(expand = expansion(c(0, 0.01)), labels = percent) +
  labs(title = "Levels of earmarking | 2012-2020",
       caption = "Source: UNHCR\n© UNHCR, The UN Refugee Agency") +
  theme_unhcr(grid = "Y", axis = "x", axis_title = FALSE)
```

</div>
<!-- End First column --->

<!-- Second column for large screen --> 
<div class="col-lg-6">


```{r r_column_stacked_100perc_chart, echo=FALSE, out.width="100%", fig.height=5.8}
# Loading data
df <- read_csv("https://raw.githubusercontent.com/GDS-ODSSS/unhcr-dataviz-platform/master/data/part_to_a_whole/column_stacked_100perc.csv")

ggplot(df) +
  geom_col(aes(x = year, y = percentage, fill = funding_type),
           width = 0.7, position = position_fill()) +
  scale_fill_unhcr_d(palette = "pal_unhcr") +
  scale_x_continuous(breaks = pretty_breaks(n = 9)) +
  scale_y_continuous(expand = expansion(c(0, 0.01)), labels = percent) +
  labs(title = "Levels of earmarking | 2012-2020",
       caption = "Source: UNHCR\n© UNHCR, The UN Refugee Agency") +
  theme_unhcr(font_size = 13, grid = "Y", axis = "x", axis_title = FALSE)
```

</div>
<!-- End Second column --->

</div>
</section>
<!-- End of section --->

<!-- To add sections just copy the whole code between the above section tag --->

</main>
